Refinements for open automata

### 2022-03-10 2021-Refinement/paper/refinementarticle.tex
correction + avancement preuve thm 3

\usepackage{tikz,mathpartir}

\usepackage{amsmath,amssymb,mathabx}
%\usepackage{amsthm}
%\usepackage{unicode-math}
\usepackage{tikz}
\usetikzlibrary{external}
\usepackage{hyperref}
\usepackage{nccrules}
\usepackage{mathtools}
\AtBeginDocument{\renewcommand\setminus{\smallsetminus}}

@@

Because of the domain of the substitutions of the relations, we have:
V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}} \vdash\\
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\mpar{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$. We need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$ with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1} \uplus  \biguplus_\subbox{p \in P} \fvars{t_{2px}} \vdash\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1} \implies 
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
Since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$, it then implies:

@@

Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.

@@

Let $R$ be the refinement relation relating states of $A_2$ and $A_3$. 
Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
Consider any two states $s_{12} = \mpar{s_1,s^1_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming). We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigwedge_\subbox{v_1\in V_1}
 v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
Let us denote $H'=H\cup J_1 \setminus\{k\}$.
We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
\begin{enumerate}
\item We have to prove that it holds for the initial configurations:
\[\sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}\]
with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{02}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.\\
By using the fact that $R$ relates initial configurations of  $A_2$ and $A_3$, we have  the following statement:
$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and relying on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have:
\[ \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
\mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\]
Because initial valuations $\sigma_{01}^1$ and $\sigma_{01}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}\right)\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }$.

@@

\begin{align*}
		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
\end{align*}		
there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
\begin{align*}
		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
\end{align*}	
such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
By definition of composition and open automata refinement we have: 
\begin{align*}
&V_{12}= V^1_1\uplus V_3 \text{ and }
V_{13}= V^2_1\uplus V_3\\
& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13} \\
\end{align*}
We have by hypothesis $\wrel{A_2}{A_3}{H}$, then for any open transition $t_2$ in $T_2$  originating from $s_2$:
\begin{align*}
\OTx{2}{}{2}{2} \in \fOT{s_2}
\end{align*}
there exists an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{3}{x}{3x}{3x} \in \fOT{s_{3}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{3x} \cap H = J'_2 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ \mpar{R\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
		\end{array}}}  \qquad \quad (*)
\end{multline*}	
\smallskip
Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition)

@@

We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$.
\[
t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
\right)^{x\in X}\]
Recall that in this case  $k \in {J^1_{1}}^{\prime}$

* or by an the transition $t_1^2=
\OT{ s^2_1}{{s^2_1}'}{\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{ \psi^2_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
\[t_{12} = \OT{\mpar{s^2_1, s_2}}{\mpar{{s^2_1}', s'_2}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{1 \prime}_1} }}{g^2_1}{\psi^2_1}
\]
We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
As  $k \in H$ we have $k \not\in J'_{3x}$ and we build:
\[t_{13x} = \left(
\OT{\mpar{s^1_1, s_3}}{\mpar{s^2_1,s'_{2x}}}{\alpha_{3x}}{\beta_{3xj}^{j \in J'_{3x}}}{g_{3x}}{\psi_{3x}} \right)^{x\in X}\]

According to how the transition $t_{12}$ is built we have to consider both cases to prove the following:
 $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in {J^1_{1}}^{\prime}:\quad &  J'_{13} \cap H'  
=((J^{2 \prime}_{1} \uplus J'_{3x}) \setminus \mbrc{k}) \cap ((H\uplus J_1) \setminus\{k\} )\\
& =((J^{2 \prime}_{1} \cap (H\uplus J_1)) \uplus (J'_{3x} \cap  (H\uplus J_1)))\setminus \mbrc{k}\\
& =((J^{2 \prime}_{1} \cap  J_1)) \uplus (J'_{3x} \cap H))\setminus \mbrc{k}\text{ since }  J^{2 \prime}_{1}\cap H = \emptyset \text{ and } J'_{3x}\cap J_1 = \emptyset  \\
& =(J^{2 \prime}_{1} \uplus (J'_{3x} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}\subseteq J_1\\
& =(J^{1 \prime}_{1} \uplus (J'_{2} \cap H))\setminus \mbrc{k}  \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
&  =((J^{1 \prime}_{1} \cap J_{1}) \uplus (J'_{2} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1} \subseteq J_1 \\
& = (J'_{2} \cap (J_1 \uplus H)) \uplus (J^{1 \prime}_{1}\cap (J_1 \uplus H))\setminus \mbrc{k} \text{ since } 
J_1 \cap  J'_{2}= \emptyset \text{ and } H \cap J^{1 \prime}_{1} = \emptyset\\
& = ((J'_{2} \uplus J^{1 \prime}_{1})\setminus \mbrc{k}) \cap   ((J_1 \uplus H)\setminus \mbrc{k})\\
& = J'_{12}\cap H'\\
\text{if } k \notin {J^1_{1}}^{\prime}:\quad &	J'_{13x} \cap H'  = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
& = \mpar{J'_2\cap H } \text{ since } J'_2 \cap H = J'_{3x} \cap H\\
& = \mpar{J'_{12}\cap H' } \text{ since } J_2\cap J'_1=\emptyset \land k\not\in {J^1_{1}}^{\prime}
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in {J^1_{1}}^{\prime}$:\\
As before, the proof  is based  on the fact that the composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$, so we deduce: 
$\alpha_{12} = \alpha_{13x}$. In addition we have:\\
 $\beta_{12j}^{j\in J'_{12}}= {{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }$\\

Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J_2 \land \beta_{2j} = \beta_{3xj})  \]\\
Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{12}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$
\end{itemize}

>>>>

\usepackage{tikz,mathpartir}
\usepackage{mathtools}
\usepackage{amsmath,amssymb,mathabx}
%\usepackage{unicode-math}
\usepackage{tikz}
\usetikzlibrary{external}
\usepackage{hyperref}
\usepackage{nccrules}

\AtBeginDocument{\renewcommand\setminus{\smallsetminus}}

@@

Because of the domain of the substitutions of the relations, we have:
\begin{multline*}
V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}} \vdash\\
R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\mpar{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}
This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$. We need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$ with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
\begin{multline*}
V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1} \uplus  \biguplus_\subbox{p \in P} \fvars{t_{2px}} \vdash\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1} \implies 
\hspace{5.5cm}\\
\operatorname*{\bigsymb{\bigvee}}_{p\in P}
\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
\mpar{\everymath{\displaystyle}
\begin{array}{l}
\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
\end{array}}
\end{multline*}
Since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$, it then implies:

@@

Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.

@@

Let $R$ be the refinement relation relating states of $A_2$ and $A_3$. 
Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
Consider any two states $s_{12} = \mpar{s^1_1,s_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming). We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigwedge_\subbox{v_1\in V_1}
 v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
Let us denote $H'=H\cup J_1 \setminus\{k\}$.
We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
\begin{enumerate}
\item We have to prove that it holds for the initial configurations:
\[\sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}\]
with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{02}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.\\
By using the fact that $R$ relates initial configurations of  $A_2$ and $A_3$, we have  the following statement:
$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and relying on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have:
\[ \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
\mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\]
Because initial valuations $\sigma_{01}^1$ and $\sigma_{01}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}\right)\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }$.

@@

\begin{align*}
		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
\end{align*}		
there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
\begin{align*}
		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
\end{align*}	
such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
By definition of composition and open automata refinement we have: 
\begin{align*}
&V_{12}= V^1_1\uplus V_2 \text{ and }
V_{13}= V^2_1\uplus V_3\\
& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13} \\
\end{align*}
We have by hypothesis $\wrel{A_2}{A_3}{H}$, then for any open transition $t_2$ in $T_2$  originating from $s_2$:
\begin{align*}
\OTx{2}{}{2}{2} \in \fOT{s_2}
\end{align*}
there exists an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{3}{x}{3x}{3x} \in \fOT{s_{3}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{3x} \cap H = J'_2 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ \mpar{R\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
		\end{array}}}  \qquad \quad (*)
\end{multline*}	
\smallskip
Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition)

@@

We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$.
\[
t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{{j \in J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x}  } }{ g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x} =  \beta^2_{1k}}{\psi_{3x} \uplus \psi^2_1}
\right)^{x\in X}\]
Recall that in this case  $k \in {J^1_{1}}^{\prime}$

* or by an the transition $t_1^1=
\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
\]
We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
As  $k \in H$ we have $k \not\in J'_{3x}$ and we build with the same transitions of $A_1$ (up renaming):
\[t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_1}', s_{3}}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1} \right)^{x\in X}\]

According to how the transition $t_{12}$ is built we have to consider both cases to prove the following:
 $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in {J^1_{1}}^{\prime}:\quad &  J'_{13} \cap H'  
=((J^{2 \prime}_{1} \uplus J'_{3x}) \setminus \mbrc{k}) \cap ((H\uplus J_1) \setminus\{k\} )\\
& =((J^{2 \prime}_{1} \cap (H\uplus J_1)) \uplus (J'_{3x} \cap  (H\uplus J_1)))\setminus \mbrc{k}\\
& =((J^{2 \prime}_{1} \cap  J_1)) \uplus (J'_{3x} \cap H))\setminus \mbrc{k}\text{ since }  J^{2 \prime}_{1}\cap H = \emptyset \text{ and } J'_{3x}\cap J_1 = \emptyset  \\
& =(J^{2 \prime}_{1} \uplus (J'_{3x} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}\subseteq J_1\\
& =(J^{1 \prime}_{1} \uplus (J'_{2} \cap H))\setminus \mbrc{k}  \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
&  =((J^{1 \prime}_{1} \cap J_{1}) \uplus (J'_{2} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1} \subseteq J_1 \\
& = (J'_{2} \cap (J_1 \uplus H)) \uplus (J^{1 \prime}_{1}\cap (J_1 \uplus H))\setminus \mbrc{k} \text{ since } 
J_1 \cap  J'_{2}= \emptyset \text{ and } H \cap J^{1 \prime}_{1} = \emptyset\\
& = ((J'_{2} \uplus J^{1 \prime}_{1})\setminus \mbrc{k}) \cap   ((J_1 \uplus H)\setminus \mbrc{k})\\
& = J'_{12}\cap H'\\
\text{if } k \notin {J^1_{1}}^{\prime}:\quad &	J'_{13x} \cap H'  = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
& = \mpar{J'_2\cap H } \text{ since } J'_2 \cap H = J'_{3x} \cap H\\
& = \mpar{J'_{12}\cap H' } \text{ since } J_2\cap J'_1=\emptyset \land k\not\in {J^1_{1}}^{\prime}
\end{align*}
For the rest of the formula we will also consider the two cases separately. 
\begin{itemize}
\item if $k \in {J^1_{1}}^{\prime}$:\\
As before, the proof  is based  on the fact that the composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. As  $\alpha^1_{1}=\alpha^2_{1}$  we deduce: 
$\alpha_{12} = \alpha_{13x}$. In addition we have:\\
 $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$\\

Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]\\
Third, considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{1}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$.

Suppose that  $V_{2} \uplus V_{3} \uplus \fvars{t_{3x}}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}}$ holds then we can deduce:
\begin{align*}
V^1_{1} \uplus V^2_{1} \uplus V_{2} \uplus V_{3} \uplus \fvars{t_{13x}}
\vdash &   \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j} \vee  
\bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}\\
\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}}\vdash & 
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{3x}   \cap H)\uplus J^{1 \prime}_1 } \beta_{12j} = \beta_{13xj}} \\  
\Rightarrow   V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash & 
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
\implies 
{\displaystyle \bigwedge_\subbox{j \in ((J'_{3x}   \cap H)\uplus J^{1 \prime}_1)\setminus \{k\} } \beta_{12j} = \beta_{13xj}}\\
\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash & 
\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
\implies 
{\displaystyle \bigwedge_\subbox{j \in (J'_{13x}   \cap H')} \beta_{12j} = \beta_{13xj}}
\end{align*}
Moreover, from the composition we deduce:
$g_{12} \Leftrightarrow g^1_1 \wedge g_2 \wedge \alpha_2=\beta^1_{1k}$ and $g_{13x}  \Leftrightarrow g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x}=\beta^2_{1k}$. 
Furthermore, as    
$\beta^1_{1k} = \beta^2_{1k}$ then we  deduce:
$ g^1_1  \wedge \alpha_2=\beta^1_{1k}  \Leftrightarrow g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}$.
